Supplementary Information

### 2021-09-17 doc/manuscript/ForestGEO_treerings.Rmd
add ORCID IDs

[Kristina J. Anderson-Teixeira](https://orcid.org/0000-0001-8461-9713)^1,2^*,
Valentine Herrmann^1^,
Christine R. Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
[M. Ross Alexander](https://orcid.org/0000-0003-1106-1100)^5^**,
Craig D. Allen^6^,
Raquel Alfaro-Sánchez^7^,
Tala Awada^8^,
Jennifer L. Baltzer^7^,
Patrick J. Baker^9^,
[Joseph D. Birch](https://orcid.org/0000-0001-8644-7345)^10^,
Sarayudh Bunyavejchewin^11^,
Paolo Cherubini^12,13^,
Stuart J. Davies^2^,
Cameron Dow^1,14^,
Ryan Helcoski^1^,
[Jakub Kašpar](https://orcid.org/0000-0003-1780-6310)^15^,
[James A. Lutz]( https://orcid.org/0000-0002-2560-0710)^16^,
Ellis Q. Margolis^17^,
Justin T. Maxwell^18^,
Sean McMahon^2,19^,
Camille Piponiot^1,2,20^,
Sabrina E. Russo^21,22^,
[Pavel Šamonil](https://orcid.org/0000-0002-7722-8797)^15^,
Anastasia E. Sniderhan^7^,
[Alan J. Tepley](https://orcid.org/0000-0002-5701-9613)^1,23^,
[Ivana Vašíčková](https://orcid.org/0000-0002-6070-5956)^15^, 
Mart Vlam^24^,
[Pieter A. Zuidema](https://orcid.org/0000-0001-8100-1168)^24^

>>>>

Kristina J. Anderson-Teixeira^1,2^* ( Orcid ID : 0000-0001-8461-9713)

Valentine Herrmann^1^ ( Orcid ID : 0000-0002-4519-481X)

Christine R. Rollinson^3^ (Orcid ID : 0000-0003-0181-7293)

Bianca Gonzalez^1^

Erika B. Gonzalez-Akre^1^ ( Orcid ID : 0000-0001-8305-6672)

Neil Pederson^4^ (Orcid ID : 0000-0003-3830-263X)

M. Ross Alexander^5^** ( Orcid ID : 0000-0003-1106-1100)

Craig D. Allen^6^  ( Orcid ID : 0000-0002-8777-5989)

Raquel Alfaro-Sánchez^7^ ( Orcid ID : 0000-0001-7357-3027)

Tala Awada^8^

Jennifer L. Baltzer^7^ ( Orcid ID : 0000-0001-7476-5928)

Patrick J. Baker^9^ ( Orcid ID : 0000-0002-6560-7124)

Joseph D. Birch ( Orcid ID : 0000-0001-8644-7345)^10^

Sarayudh Bunyavejchewin^11^ ( Orcid ID : 0000-0002-1976-5041)

Paolo Cherubini^12,13^ ( Orcid ID : 0000-0002-9809-250X)

Stuart J. Davies^2^

Cameron Dow^1,14^

Ryan Helcoski^1^

Jakub Kašpar^15^ ( Orcid ID : 0000-0003-1780-6310)

James A. Lutz^16^ (  Orcid ID : 0000-0002-2560-0710)

Ellis Q. Margolis^17^ ( Orcid ID :  0000-0002-0595-9005)

Justin T. Maxwell^18^ ( Orcid ID : 0000-0001-9195-3146)

Sean McMahon^2,19^  (Orcid ID : 0000-0001-8302-6908)

Camille Piponiot^1,2,20^ (Orcid ID : 0000-0002-3473-1982)

Sabrina E. Russo^21,22^ (Orcid ID : 0000-0002-6788-2410)

Pavel Šamonil^15^ ( Orcid ID : 0000-0002-7722-8797)

Anastasia E. Sniderhan^7^

Alan J. Tepley^1,23^ ( Orcid ID : 0000-0002-5701-9613)

Ivana Vašíčková^15^ ( Orcid ID : 0000-0002-6070-5956)

Mart Vlam^24^

Pieter A. Zuidema^24^ ( Orcid ID : 0000-0001-8100-1168)
